---
title: "Downstream analysis, dataset: `r params$dataset.name`, config version `r params$config.version`"
author:
  - "trnguyen@ukaachen.de"
date: "Last update on `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 3
    theme: lumen
params:
  config.version: NA
  orig.dataset: NA
  output.version: NA
---
  
```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
$(document).ready(function() {
  $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
  // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

<style type="text/css">
    div.datatables { height: auto !important;}
</style>



```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
##### clean up #####
# gc()
# rm(list = ls())

path.to.project.src <- "/media/hieunguyen/HNSD01/src/migratory_ccr7_data_analysis"

source(file.path(path.to.project.src, "import_libraries.R"))
source(file.path(path.to.project.src, "helper_functions.R"))
source(file.path(path.to.project.src, "config.R"))

#####----------------------------------------------------------------------#####
# CONFIGURATIONS AND PREPRATIONS
#####----------------------------------------------------------------------#####
# outdir <- "/media/hieunguyen/HD0/outdir/CRC1382"

outdir <- "/media/hieunguyen/HNSD01/outdir"

orig.dataset <- params$orig.dataset
config.version <- params$config.version
output.version <- params$output.version

PROJECT <- "FHager_datasets"

input.config <- config.params[[config.version]]
dataset.name <- sprintf("%s_%s", orig.dataset, config.version)

if (orig.dataset == "integrate_GSE192742_LIVER"){
  path.to.main.input <- file.path(outdir,
                                PROJECT,
                                output.version, 
                                dataset.name, 
                                "s8_output",
                                sprintf("%s.output.s8.rds", dataset.name))
} else {
  path.to.main.input <- file.path(outdir,
                                PROJECT,
                                output.version, 
                                dataset.name, 
                                "s8a_output",
                                sprintf("%s.output.s8a.rds", dataset.name))
}


path.to.main.output <- file.path(outdir, PROJECT, output.version, dataset.name, "data_analysis")
dir.create(path.to.main.output, showWarnings = FALSE)

s.obj <- readRDS(path.to.main.input)

path.to.01.output <- file.path(path.to.main.output, "01_output")
dir.create(path.to.01.output, showWarnings = FALSE, recursive = TRUE)
```

# Preprocessing and QC
## Raw data Quality control  {.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (plot.name in names(s.obj@misc$all.QC)){
 
    cat('###',plot.name,'{.unlisted .unnumbered} \n')
    
    ##### 
    # plots or tables that we want to show in tabs
    #####
    print(s.obj@misc$all.QC[plot.name])
    cat(' \n \n')
}
```

## Ambient RNA background correction 

### DecontX clusters {.tabset}
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (plot.name in names(s.obj@misc$ambient.cluster.RNA.plot)){
 
    cat('####',plot.name,'{.unlisted .unnumbered} \n')
    
    ##### 
    # plots or tables that we want to show in tabs
    #####
    print(s.obj@misc$ambient.cluster.RNA.plot[plot.name])
    cat(' \n \n')
}
```

### Contamination level in each sample

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
ggplot(s.obj@meta.data, aes(x=name, y=AmbientRNA)) + 
  geom_boxplot()

```


### Ambient RNA contamination level {.tabset}

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (plot.name in names(s.obj@misc$ambient.contamination.plot)){
 
    cat('####',plot.name,'{.unlisted .unnumbered} \n')
    
    ##### 
    # plots or tables that we want to show in tabs
    #####
    print(s.obj@misc$ambient.contamination.plot[plot.name])
    cat(' \n \n')
}
```


## Descriptive statistics and filtering threshold {.tabset}
This section is devoted to the descriptive statistics of the following varialbes: `nFeature_RNA, nCount_RNA, percent.mt, percent.ribo`. 

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (plot.item in c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.ribo")){
  boxplot <- s.obj@meta.data %>% ggplot(aes_string(x = "name", y = plot.item)) +
    geom_boxplot(outlier.colour="black", outlier.shape=16,
               outlier.size=2, notch=FALSE) +
    ggtitle(sprintf("Boxplot: Distribution of %s in each dataset", plot.item))
  cat('###', plot.item,'{.unlisted .unnumbered} \n')
    
    ##### 
    # plots or tables that we want to show in tabs
    #####
  
  print(boxplot)
  
  cat(' \n \n')
}
```



## Descriptive statistics + UMAP {.tabset}

### % Mitochondrial
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, reduction = "RNA_UMAP", feature = "percent.mt", label = TRUE, label.size = 8, pt.size = 0.5, label.color = "red", )
```

### % Ribosome
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, reduction = "RNA_UMAP", feature = "percent.ribo", label = TRUE, label.size = 8, pt.size = 0.5, label.color = "red", )
```

### % nCount RNA
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, reduction = "RNA_UMAP", feature = "nCount_RNA", label = TRUE, label.size = 8, pt.size = 0.5, label.color = "red", )
```

### % nGenes 
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, reduction = "RNA_UMAP", feature = "nFeature_RNA", label = TRUE, label.size = 8, pt.size = 0.5, label.color = "red", )
```

## Cell cycle scoring {.tabset}

### Cell cycle, split by Phase
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(s.obj, reduction = "RNA_UMAP", split.by = "Phase")
```

### Cell cycle, group by Phase
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
DimPlot(s.obj, reduction = "RNA_UMAP", group.by = "Phase", label = TRUE, label.size = 8, pt.size = 0.5, label.box = TRUE, repel = TRUE)
```

### PCA, cell cycle, group by Phase
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
all.genes <- rownames(x = s.obj)
s.genes <- paste0("^", cc.genes$s.genes, "$", collapse = "|")
s.genes <- all.genes[grepl(s.genes, all.genes, ignore.case = TRUE)]
g2m.genes <- paste0("^", cc.genes$g2m.genes, "$", collapse = "|")
g2m.genes <- all.genes[grepl(g2m.genes, all.genes, ignore.case = TRUE)]
s.obj <- RunPCA(s.obj, features = c(s.genes, g2m.genes), nfeatures.print = 10, reduction.name="CELLCYCLED_PCA")

DimPlot(s.obj, reduction = "CELLCYCLED_PCA", group.by = "Phase", pt.size = 1)
```



# Count number of cells having EGFP gene expression

## UMAP: distribution of cells having CCR7 or EGFP
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
if (orig.dataset == "gutcellatlas_myeloid"){
  FeaturePlot(s.obj, features = c("CCR7", "EGFP"), slot = "data", label = TRUE, label.size = 6, label.color = "red")
} else {
  FeaturePlot(s.obj, features = c("Ccr7", "EGFP"), slot = "data", label = TRUE, label.size = 6, label.color = "red")  
}

```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
EGFP.cells <- GetAssayData(s.obj, slot = "counts")["EGFP", ]
EGFP.cells <- names(EGFP.cells[EGFP.cells != 0])
print(sprintf("Number of cells having expression at EGFP: %s \n", length(EGFP.cells)))
```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
if (orig.dataset == "gutcellatlas_myeloid"){ 
  ccr7.cells <- GetAssayData(s.obj, slot = "counts")["CCR7", ]
} else {
  ccr7.cells <- GetAssayData(s.obj, slot = "counts")["Ccr7", ]
}


ccr7.cells <- names(ccr7.cells[ccr7.cells != 0])

intersection_ccr7_EGFP <- intersect(EGFP.cells, ccr7.cells)
print(sprintf("Number of cells having expression at Ccr7: %s \n", length(ccr7.cells)))
```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
print(sprintf("Number of cells having both CCR7 and EGFP: %s \n", length(intersection_ccr7_EGFP)))
```

## UMAP highlighting cells having both CCR7 and EGFP
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
DimPlot(s.obj, reduction = "RNA_UMAP", cells.highlight = intersection_ccr7_EGFP, label = TRUE, label.box = TRUE, repel = TRUE) +
  theme(legend.position = "none") + ggtitle("Highlighted cells having both CCR7 and EGFP expressions")
```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
p.EGFP.cells <- DimPlot(s.obj, reduction = "RNA_UMAP", cells.highlight = EGFP.cells, label = TRUE, label.box = TRUE, repel = TRUE) +
  ggtitle("Cells expressing EGFP") + theme(legend.position = "none")
  
p.Ccr7.cells <- DimPlot(s.obj, reduction = "RNA_UMAP", cells.highlight = ccr7.cells, label = TRUE, label.box = TRUE, repel = TRUE) +
  ggtitle("Cells expressing Ccr7") + theme(legend.position = "none")

p.EGFP.cells + p.Ccr7.cells
```

# Dimensional reduction UMAP 
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
DimPlot(object = s.obj, reduction = "RNA_UMAP", label = TRUE, label.box = TRUE, repel = TRUE) +
  ggtitle("UMAP, all cells, group by clusters")

cluster7.cells <- row.names(subset(s.obj@meta.data, s.obj@meta.data$seurat_clusters == 7))
```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
p <- DimPlot(object = s.obj, reduction = "RNA_UMAP", label = TRUE, label.box = TRUE, repel = TRUE, label.size = 10, pt.size = 1) +
  theme(axis.text = element_text(size=20, face = "bold"),
        axis.title = element_text(size=20, face = "bold"), 
        title = element_text(size = 20, face = "bold"), 
        legend.text = element_text(size = 20))

ggsave(plot = p, filename = "UMAP_all_cells.png", dpi = 300, height = 10, width = 12, device = "png", path = ".")
```

# Re-clustering with higher cluster resolution
Default cluster resolution is 0.5, we perform re-clustering with resolution of 1.

## All cells
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
cluster.resolution <- 1

num.PCA <- 25
num.PC.used.in.UMAP <- 25
num.PC.used.in.Clustering <- 25
chosen.assay <- "RNA"
my_random_seed <- 42

s.obj <- FindNeighbors(s.obj, reduction = sprintf("%s_PCA", chosen.assay), dims = 1:num.PC.used.in.Clustering)
  
s.obj <- FindClusters(s.obj, resolution = cluster.resolution, random.seed = 0)

old.cluster.info <- s.obj@meta.data %>% subset(select = c(seurat_clusters)) 
```


### Dimensional reduction UMAP after reclustering
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.height=10, fig.width=18, dpi = 300}
DimPlot(object = s.obj, reduction = "RNA_UMAP", label = TRUE, label.box = TRUE, repel = TRUE) +
  ggtitle("UMAP, all cells, group by clusters")
```

# Cluster marker genes

Applying the `wilcox` test on all genes to find the highly expressed genes in each cluster. 

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
if (file.exists(file.path(path.to.01.output, "cluster_markers.rds")) == FALSE){
  cluster.markers <- FindAllMarkers(object = s.obj, assay = "RNA", test.use = "wilcox")
  cluster.markers <- subset(cluster.markers, cluster.markers$p_val_adj <= 0.05)
  saveRDS(cluster.markers, file.path(path.to.01.output, "cluster_markers.rds"))  
} else {
  cluster.markers <- readRDS(file.path(path.to.01.output, "cluster_markers.rds"))
}
```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
```

## Tables of all cluster marker genes {.tabset}
```{r echo=FALSE, include=FALSE}
cluster.markers %>% create_dt()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}

for (cluster.id in sort(unique(cluster.markers$cluster))){
  tmp.cluster.markers <- subset(cluster.markers, cluster.markers$cluster == cluster.id) %>% arrange(desc(avg_log2FC))
  tmp.cluster.markers <- tmp.cluster.markers %>% mutate_if(is.numeric, round, 6) 
  
  cat(paste("\n\n### Cluster: ", cluster.id, "##\n"))
  print( htmltools::tagList(datatable(tmp.cluster.markers, extensions = 'Buttons',
                filter = "top",
                options = list(dom = 'Blfrtip',
                               buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                               lengthMenu = list(c(10,25,50,-1),
                                                 c(10,25,50,"All")),
                               columnDefs = list(list(
                                 targets = "_all",
                                 render = JS(
                                   "function(data, type, row, meta) {",
                                   "return type === 'display' && data != null && data.length > 100 ?",
                                   "'<span title=\"' + data + '\">' + data.substr(0, 100) + '...</span>' : data;",
                                   "}")
                               ))
                ))))
  cat("\n \n")
}

```

## Top-12 cluster marker genes `FeaturePlot` {.tabset}
Here we just show the top-12 genes (ranked by `avg_log2FC`) for each cluster. 

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
for (cluster.id in sort(unique(s.obj@meta.data$seurat_clusters))){
  DefaultAssay(s.obj) <- "RNA"
  cat(sprintf("### Cluster %s \n", cluster.id))
  tmp.cluster.markers <- subset(cluster.markers, cluster.markers$cluster == cluster.id) %>% arrange(desc(avg_log2FC))
  p <- FeaturePlot(object = s.obj, reduction = "RNA_UMAP", features = head(tmp.cluster.markers, 9)$gene, ncol = 3, label = TRUE, pt.size = 0.5, label.size = 5, label.color = "red")  
  print(p)
  cat("\n \n")
}
```

## Number of cells in each cluster (all clusters)
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
count.cell.in.clusters <- s.obj@meta.data %>% subset(select = seurat_clusters) %>% table() %>% as.data.frame()
colnames(count.cell.in.clusters) <- c("cluster", "count")
total <- sum(count.cell.in.clusters$count)
count.cell.in.clusters <- count.cell.in.clusters %>% rowwise() %>% mutate(pct = 100 * count/total)

count.cell.in.clusters %>% arrange(desc(pct)) %>% create_dt()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
if (file.exists(file.path(path.to.01.output, sprintf("%s.rds", dataset.name))) == FALSE){
  saveRDS(s.obj, file.path(path.to.01.output, sprintf("%s.rds", dataset.name)))  
}
```

# Extract CCR7 cluster only and run sub-clustering

## UMAP, 2 new sub clusters in cluster CCR7
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=14, fig.height=10}
meta.data <- s.obj@meta.data %>% rownames_to_column("barcode")
meta.data.ccr7 <- subset(meta.data, meta.data$barcode %in% intersect(ccr7.cells, EGFP.cells))

ccr7.cluster.idx <- table(meta.data.ccr7$seurat_clusters)[table(meta.data.ccr7$seurat_clusters) == max(table(meta.data.ccr7$seurat_clusters))] %>% names()
cluster.resolution <- 1
s.obj.selected.CCR7 <- subset(s.obj, seurat_clusters == ccr7.cluster.idx)
s.obj.selected.CCR7 <- RunPCA(s.obj.selected.CCR7, npcs = num.PCA, verbose = FALSE, reduction.name = "RNA_PCA")
s.obj.selected.CCR7 <- RunUMAP(s.obj.selected.CCR7, reduction = "RNA_PCA", 
                       dims = 1:num.PC.used.in.UMAP, reduction.name = "RNA_UMAP",
                       seed.use = my_random_seed, umap.method = "uwot")
s.obj.selected.CCR7 <- FindNeighbors(s.obj.selected.CCR7, reduction = "RNA_PCA", dims = 1:num.PC.used.in.Clustering)
s.obj.selected.CCR7 <- FindClusters(s.obj.selected.CCR7, resolution = cluster.resolution, random.seed = 0)

sub.cluster.ccr7.cells <- list()
for (idx in unique(s.obj.selected.CCR7$seurat_clusters)){
  sub.cluster.ccr7.cells[[idx]] <- subset(s.obj.selected.CCR7, seurat_clusters == idx) %>% colnames()
}
names(sub.cluster.ccr7.cells) <- unique(s.obj.selected.CCR7$seurat_clusters)
library(scales)

DimPlot(object = s.obj, reduction = "RNA_UMAP", 
        cells.highlight = sub.cluster.ccr7.cells, 
        cols.highlight = hue_pal()(length(names(sub.cluster.ccr7.cells))),
        label = TRUE, label.box = TRUE)
```


```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=14, fig.height=10}
meta.data <- s.obj@meta.data %>% rownames_to_column("barcode") %>%
  rowwise() %>%
  mutate(ccr7.cluster = case_when(barcode %in% sub.cluster.ccr7.cells$`0` ~ "CCR7_cluster0",
                                  barcode %in% sub.cluster.ccr7.cells$`1` ~ "CCR7_cluster1",
                                  barcode %in% c(sub.cluster.ccr7.cells$`0`, sub.cluster.ccr7.cells$`1`) == FALSE ~ "others")) %>%
  column_to_rownames("barcode")
meta.data <- meta.data[row.names(s.obj@meta.data), ]
s.obj <- AddMetaData(object = s.obj, metadata = meta.data$ccr7.cluster, col.name = "ccr7_cluster")

if (file.exists(file.path(path.to.01.output, sprintf("%s.CCR7_cluster.rds", dataset.name))) == FALSE){
  saveRDS(s.obj, file.path(path.to.01.output, sprintf("%s.CCR7_cluster.rds", dataset.name)))  
}
```

## Cluster marker genes
Applying the `wilcox` test on all genes to find the highly expressed genes in each cluster.

- **Positive** logFC indicates that the gene is up in the `subcluster` 0 of cluster 9.

- **Negative** logFC indicates that the gene is up in the `subcluster` 1 of cluster 9.

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
cluster9.diff.markers <- FindMarkers(object = s.obj.selected.CCR7, ident.1 = 0, ident.2 = 1, group.by = "seurat_clusters")
cluster9.diff.markers.raw <- cluster9.diff.markers
cluster9.diff.markers <- subset(cluster9.diff.markers, cluster9.diff.markers$p_val_adj <= 0.05) %>%
  rownames_to_column("Gene")

cluster9.diff.markers %>% mutate_if(is.numeric, round, 6) %>% create_dt()
```

## Violin plot for top 10 genes up/down in subcluster 0 of cluster 9

### Top 10 up genes in subcluster 0 of cluster 9
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=14, fig.height=10}
top10.up.genes <- subset(cluster9.diff.markers, cluster9.diff.markers$avg_log2FC >=0) %>% head()
if (nrow(top10.up.genes) > 0){
  VlnPlot(object = s.obj.selected.CCR7, features = top10.up.genes$Gene)  
} else {
  ggplot() + ggtitle("No gene found")
}

```

### Top 10 down genes in subcluster 0 of cluster 9 (up in subcluster 1)
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
top10.down.genes <- subset(cluster9.diff.markers, cluster9.diff.markers$avg_log2FC < 0) %>% 
  arrange(desc(avg_log2FC)) %>% tail(10)

if (nrow(top10.down.genes) > 0){
  VlnPlot(object = s.obj.selected.CCR7, features = top10.down.genes$Gene)
} else {
  ggplot() + ggtitle("No gene found")
}

```

## UMAP feature plot for top 10 genes up/down in subcluster 0 of cluster 9

### Top 10 up genes in subcluster 0 of cluster 9
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=14, fig.height=10}
top10.up.genes <- subset(cluster9.diff.markers, cluster9.diff.markers$avg_log2FC >=0) %>% head()
if (nrow(top10.up.genes) > 0){
  FeaturePlot(object = s.obj, features = top10.up.genes$Gene, reduction = "RNA_UMAP", label = TRUE)    
} else {
  ggplot() + ggtitle("No gene found")
}

```

### Top 10 down genes in subcluster 0 of cluster 9 (up in subcluster 1)
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
top10.down.genes <- subset(cluster9.diff.markers, cluster9.diff.markers$avg_log2FC < 0) %>% 
  arrange(desc(avg_log2FC)) %>% tail(10)
if (nrow(top10.down.genes) > 0){
  FeaturePlot(object = s.obj, features = top10.down.genes$Gene, reduction = "RNA_UMAP", label = TRUE)  
} else {
  ggplot() + ggtitle("No gene found")
}

```

## Check "Xcr1", "Irf8", "Sirpa", "Itgam", "Irf4"
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
subset(cluster9.diff.markers.raw, cluster9.diff.markers.raw$Gene %in% c("Xcr1", "Irf8", "Sirpa", "Itgam", "Irf4")) %>% create_dt()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
FeaturePlot(object = s.obj, features = c("Xcr1", "Irf8", "Sirpa", "Itgam", "Irf4"), reduction = "RNA_UMAP", label = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=20, fig.height=12}
count.cell.new <- table(s.obj$seurat_clusters) %>% data.frame()
colnames(count.cell.new) <- c("cluster", "count")
count.cell.new %>% create_dt()
```
