---
title: "Dataset GSE71170 (microarray, Lung (Immature/Mature), Thymus (Immature, Mature))"
author:
  - "trnguyen@ukaachen.de"
date: "Last update on `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 3
    number_sections: false
    theme: lumen
---

Raw data GSE71170 (`.CEL` files) were downloaded from https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE71171


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
gc()
rm(list = ls())

path.to.project.src <- "/media/hieunguyen/HNSD01/src/migratory_ccr7_data_analysis/microarray_data"
source(file.path(path.to.project.src, "import_libraries.R"))

dataset_gse <- "GSE71170"
output.version <- "20240806"

outdir <- "/media/hieunguyen/HNSD01/outdir"
PROJECT <- "FHager_datasets"

path.to.main.output <- file.path(outdir, PROJECT, output.version, "microarray_output", dataset_gse)
dir.create(path.to.main.output, showWarnings = FALSE, recursive = TRUE)

path.to.01.output <- file.path(path.to.main.output, "01_output")

path.to.02.output <- file.path(path.to.main.output, "02_output")
dir.create(path.to.02.output, showWarnings = FALSE, recursive = TRUE)

#####----------------------------------------------------------------------#####
##### Helper function for create_dt
#####----------------------------------------------------------------------#####
create_dt <- function(x){
  DT::datatable(x,
                extensions = 'Buttons',
                filter = "top",
                options = list(dom = 'Blfrtip',
                               buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                               lengthMenu = list(c(10,25,50,-1),
                                                 c(10,25,50,"All")),
                               columnDefs = list(list(
                                 targets = "_all",
                                 render = JS(
                                   "function(data, type, row, meta) {",
                                   "return type === 'display' && data != null && data.length > 100 ?",
                                   "'<span title=\"' + data + '\">' + data.substr(0, 100) + '...</span>' : data;",
                                   "}")
                               ))
                ))
}
#####----------------------------------------------------------------------#####

thymus.rma.data <- readRDS(file.path(path.to.01.output, "thymus_rma_calibrated_data_object.rds"))
thymus.rma.exprs <- readRDS(file.path(path.to.01.output, "thymus_rma_calibrated_data_exprs_table.rds"))
colnames(thymus.rma.exprs) <- to_vec(for (item in colnames(thymus.rma.exprs)) str_split(item, "_")[[1]][[1]])

lung.rma.data <- readRDS(file.path(path.to.01.output, "lung_rma_calibrated_data_object.rds"))
lung.rma.exprs <- readRDS(file.path(path.to.01.output, "lung_rma_calibrated_data_exprs_table.rds"))
colnames(lung.rma.exprs) <- to_vec(for (item in colnames(lung.rma.exprs)) str_split(item, "_")[[1]][[1]])

library(tidyverse)
library(dplyr)

GPL6246 <- readRDS(file.path(path.to.01.output, "GPL6246_preprocessed.rds"))
GPL1261 <- readRDS(file.path(path.to.01.output, "GPL1261_preprocessed.rds"))
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
```

# Lung samples
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#####----------------------------------------------------------------------#####
# LUNG SAMPLES
#####----------------------------------------------------------------------#####
lung.design.matrix <- model.matrix(~ 0 + pData(lung.rma.data)$Status)

colnames(lung.design.matrix) <- c("Immature", "Mature")

# logFC = Immature / Mature, in this makeConstrast function we will also define
# the order of the logFC.
lung.contrast_matrix <- makeContrasts(Mature-Immature, levels = lung.design.matrix) 

lung_fit <- eBayes(contrasts.fit(lmFit(lung.rma.data,
                                       design = lung.design.matrix), lung.contrast_matrix))

lung_DE_table <- topTable(lung_fit, number = Inf)

lung_DE_table <- lung_DE_table %>% 
  rownames_to_column("Gene.ID") %>% 
  rowwise %>% mutate(abs_log2FC = abs(logFC)) %>% 
  arrange(desc(abs_log2FC)) %>% mutate(Gene = paste(subset(GPL6246, GPL6246$PROBEID == Gene.ID)$SYMBOL, collapse = ", "))


```

## Metadata
Metadata was downloaded from https://www.ebi.ac.uk/biostudies/arrayexpress/studies/E-GEOD-71170#

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
pData(lung.rma.data) %>% rownames_to_column("Filename") %>% rowwise %>% mutate(Sample.name = str_split(Filename, "_")[[1]][[1]]) %>%
  subset(select = c(Sample.name, Status, Filename))%>% create_dt()
```

## Differential gene expression results

The log2FC is calculated as `Mature` over `Immature`;

- **Positive** `log2FC` indicates that the gene is **up-regulated** in **Mature** samples

- **Negative** `log2FC` indicates that the gene is **up-regulated** in **Immature** samples

Genes having **adjusted P-value** (Benjamin - Hochberg false discovery rate correction) **less than 0.05** and **log2FC greater than 1** are called significant DE genes and listed in the following table.

Table is sorted in descending order of absolute value of log2FC.

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
lung_DE_table <- lung_DE_table %>% subset(select = c(Gene.ID, logFC, AveExpr, P.Value, adj.P.Val, abs_log2FC, Gene))
lung_DE_table <- merge(lung_DE_table, lung.rma.exprs, by.x = "Gene.ID", by.y = 0)

lung_DE_table <- lung_DE_table %>% subset(adj.P.Val < 0.05 & abs_log2FC >= 1) 
lung_DE_table %>% mutate_if(is.numeric, round, 6) %>% arrange(desc(abs_log2FC))%>% create_dt()

```

<!-- ## Volcano plot -->

<!-- ```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'} -->
<!-- input.df <- lung_DE_table -->

<!-- input.df <- input.df %>% rowwise %>% mutate(sig = ifelse(adj.P.Val <= 0.05 & abs_log2FC >= 1, "Significant", "Not significant")) -->
<!-- volcano.plot <- ggplot(data=input.df,  -->
<!--                        aes(x=logFC, y=-log10(adj.P.Val), col=sig, label=Gene)) +  -->
<!--   geom_point() +  -->
<!--   scale_color_manual(values=c("#c0d2f0", "#f28095")) + -->
<!--   theme_minimal() + -->
<!--   geom_vline(xintercept=c(-1, 1), col="#9a9fa6", linetype='dotted') + -->
<!--   geom_hline(yintercept=-log10(0.05), col="#9a9fa6", linetype='dotted') + -->
<!--   xlim(-5, 5) + ylim(0, 4) +  -->
<!--   theme_bw() +  -->
<!--   theme(plot.title = element_text(hjust=0.5, face="bold", size = 12)) -->

<!-- volcano.plotly <- ggplotly(volcano.plot,  tooltip = c("x", "y", "label")) -->

<!-- volcano.plotly -->
<!-- ``` -->


# Thymus samples
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#####----------------------------------------------------------------------#####
# thymus SAMPLES
#####----------------------------------------------------------------------#####
thymus.design.matrix <- model.matrix(~ 0 + pData(thymus.rma.data)$Status)

colnames(thymus.design.matrix) <- c("Immature", "Mature")

# logFC = Immature / Mature
thymus.contrast_matrix <- makeContrasts(Mature-Immature, levels = thymus.design.matrix)

thymus_fit <- eBayes(contrasts.fit(lmFit(thymus.rma.data,
                                       design = thymus.design.matrix), thymus.contrast_matrix))

thymus_DE_table <- topTable(thymus_fit, number = Inf)

thymus_DE_table <- thymus_DE_table %>% 
  rownames_to_column("Gene.ID") %>% 
  rowwise %>% mutate(abs_log2FC = abs(logFC)) %>% 
  arrange(desc(abs_log2FC)) %>% mutate(Gene = paste(subset(GPL1261, GPL1261$ID == Gene.ID)$Gene.Symbol, collapse = ", "))
```

## Metadata
Metadata was downloaded from https://www.ebi.ac.uk/biostudies/arrayexpress/studies/E-GEOD-71170#

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
pData(thymus.rma.data) %>% rownames_to_column("Filename") %>% rowwise %>% mutate(Sample.name = str_split(Filename, "_")[[1]][[1]]) %>%
  subset(select = c(Sample.name, Status, Filename))%>% create_dt()
```

## Differential gene expression results

The log2FC is calculated as `Immature` over `Mature`;

- **Positive** `log2FC` indicates that the gene is **up-regulated** in **Mature** samples

- **Negative** `log2FC` indicates that the gene is **up-regulated** in **Immature** samples

Genes having **adjusted P-value** (Benjamin - Hochberg false discovery rate correction) **less than 0.05** and **log2FC greater than 1** are called significant DE genes and listed in the following table.

Table is sorted in descending order of absolute value of log2FC.

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
thymus_DE_table <- thymus_DE_table %>% subset(select = c(Gene.ID, logFC, AveExpr, P.Value, adj.P.Val, abs_log2FC, Gene))
thymus_DE_table <- merge(thymus_DE_table, thymus.rma.exprs, by.x = "Gene.ID", by.y = 0)

thymus_DE_table <- thymus_DE_table %>% subset(adj.P.Val < 0.05 & abs_log2FC >= 1) 
thymus_DE_table %>% mutate_if(is.numeric, round, 6) %>% arrange(desc(abs_log2FC))%>% create_dt()
```

<!-- ## Volcano plot -->

<!-- ```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'} -->
<!-- input.df <- thymus_DE_table -->

<!-- input.df <- input.df %>% rowwise %>% mutate(sig = ifelse(adj.P.Val <= 0.05 & abs_log2FC >= 1, "Significant", "Not significant")) -->
<!-- volcano.plot <- ggplot(data=input.df,  -->
<!--                        aes(x=logFC, y=-log10(adj.P.Val), col=sig, label=Gene)) +  -->
<!--   geom_point() +  -->
<!--   scale_color_manual(values=c("#c0d2f0", "#f28095")) + -->
<!--   theme_minimal() + -->
<!--   geom_vline(xintercept=c(-1, 1), col="#9a9fa6", linetype='dotted') + -->
<!--   geom_hline(yintercept=-log10(0.05), col="#9a9fa6", linetype='dotted') + -->
<!--   xlim(-5, 5) + ylim(0, 4) +  -->
<!--   theme_bw() +  -->
<!--   theme(plot.title = element_text(hjust=0.5, face="bold", size = 12)) -->

<!-- volcano.plotly <- ggplotly(volcano.plot,  tooltip = c("x", "y", "label")) -->

<!-- volcano.plotly -->
<!-- ``` -->

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
#####----------------------------------------------------------------------#####
# SAVE DATA OBJECTS FOR FURTHER ANALYSIS
#####----------------------------------------------------------------------#####
write.csv(lung_DE_table, file.path(path.to.02.output, "Lung_DE_table.csv"))
write.csv(thymus_DE_table, file.path(path.to.02.output, "Thymus_DE_table.csv"))

```
